Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-10-26 tests-ionbalance.tex

In this test, we initialize a one-dimension grid at a constant number
density of 1 cm$^{-3}$ with smoothly varying temperature from 10$^{4}$
K to 10$^{9}$ K.  The gas is initially fully ionized and we then
iterate the chemistry equations without allowing the gas to cool until
convergence is reached.  In Figure \ref{fig.eq_test}, we show the
equilibrium ionization fractions for H and He ions and the resulting
cooling rate.  We assume no photo-ionization for this test.  
The results from this test are shown by the solid lines 
with the analytic solution decribed by 
Equations \ref{eq:eqnHI}--\ref{eq:eqne} using the rate equations 
in \enzo, referenced in \s\ref{sec.num.chemistry}, overplotted with
the dashed lines and an analytical solution using the rates 
of \citet{1992ApJS...78..341C}, shown by the dotted lines.  As can be
seen, the \enzo\ chemistry solver and corresponding analytical
solution are in perfect agreement.  The results largely agree with
those of \citet{1992ApJS...78..341C}, save for HI, HeI, and HeII at
high temperatures, where their ion fractions are quite low.  The
slightly higher abundance of HeI in \citet{1992ApJS...78..341C}
results in a higher cooling rate by about a factor of 2 near $T \sim
10^{5}$ K due to the enhanced collisional excitation cooling of HeI.

>>>>

In this test, we initialize a one-dimension grid at a constant number
density of 1 cm$^{-3}$ with smoothly varying temperature from 10$^{4}$
K to 10$^{9}$ K.  The gas is initially fully ionized and we then
iterate the chemistry equations without allowing the gas to cool until
convergence is reached.  In Figure \ref{fig.eq_test}, we show the
equilibrium ionization fractions for H and He ions and the resulting
cooling rate.  We assume no photo-ionization for this test.  
The results from this test are shown by the solid lines 
with the analytic solution decribed by 
Equations \ref{eq:eqnHI}--\ref{eq:eqne} using the rate equations 
in \enzo, referenced in \S\ref{sec.num.chemistry}, overplotted with
the dashed lines and an analytical solution using the rates 
of \citet{1992ApJS...78..341C}, shown by the dotted lines.  As can be
seen, the \enzo\ chemistry solver and corresponding analytical
solution are in perfect agreement.  The results largely agree with
those of \citet{1992ApJS...78..341C}, save for HI, HeI, and HeII at
high temperatures, where their ion fractions are quite low.  The
slightly higher abundance of HeI in \citet{1992ApJS...78..341C}
results in a higher cooling rate by about a factor of 2 near $T \sim
10^{5}$ K due to the enhanced collisional excitation cooling of HeI.
